Type-Safe Modular Parsing

### 2017-01-12 paper/sections/ObjectAlgebras.tex
Fix 4.3

\paragraph{Extensions}
Now let's try this pattern with the variables extension:
\lstinputlisting[linerange=37-48]{../Scala/Parser/src/PaperCode/Sec4OA/Code3.scala}% APPLY:linerange=EXT_OA_PARSER
\bruno{break code into 2 parts: the definition of the trait; and the client 
code.}
\bruno{the following text should be for explaining the definition of the trait}
\noindent The type of the object algebra field \lstinline{alg} is first refined 
to \lstinline{VarExpAlg[E]}, to allow calling the additional factory method 
for variables. Note that, unlike the previous attempt, \lstinline{VarExpAlg[E]}
is a subtype of \lstinline{ExpAlg[E]}, thus the type-refinement of the 
field is allowed. Now, the code for parsing variables (\lstinline{pVar}) can 
call \lstinline{alg.varE}. The following code illustrates how to use 
the parser from a client perspective:

\bruno{put the client code here.}

\bruno{have we defined the ``parse'' method?? I don't think we have!
We need to first present the parse method. }
In the client code shown above, we first need to chose a concrete 
object algebra to initialize the \lstinline{alg} field in \lstinline{VarExprOAParser}. Here we pick the 
pretty-printing algebra \lstinline{VarExprPrint}, but any other object 
algebra that implements \lstinline{VarExprAlg} would work. 
With an instance of \lstinline{VarExprOAParser} in hand, we can call 
\lstinline{pE} to obtain the parser to feed to the \lstinline{parse} method. 
The result shows that such a pattern provides modular parsing.

@@

Figure~\ref{fig:multi} illustrates the corresponding Scala code 
that extends the Object Algebra interface, pretty-printing operation and parser. We use two type parameters \inlinecode{E} and \inlinecode{T} for expressions and types. They guarantee that invalid terms such as \inlinecode{int + int} will be rejected by the parser.
Besides lexing, the trait \inlinecode{TypedLamOAParser} also introduces parsers for types, and the new case for expressions. 
We use \inlinecode{pTypedLamT} and \inlinecode{pTypedLamE} as copies of current \inlinecode{pT} and \inlinecode{pE}, due to the issue 
with \lstinline{super} in Scala (see discussion in Section~\ref{subsec:parsingwithoa}). \inlinecode{pT} and \inlinecode{pE} are the parsers used for performing recursion.

@@

\lstinputlisting[linerange=63-65]{../Scala/Parser/src/PaperCode/Sec4OA/Code4.scala}% APPLY:linerange=OVERVIEW_OA_MULTI_SYNTAX_CLIENT
The code works as expected to parse and pretty-print the result.

>>>>

\paragraph{Extensions}
Now let's try this pattern with the variables extension:
\lstinputlisting[linerange=37-44]{../Scala/Parser/src/PaperCode/Sec4OA/Code3.scala}% APPLY:linerange=EXT_OA_PARSER
\huang{done}\bruno{break code into 2 parts: the definition of the trait; and the client
code.}
\bruno{the following text should be for explaining the definition of the trait}
\noindent The type of the object algebra field \lstinline{alg} is first refined
to \lstinline{VarExpAlg[E]}, to allow calling the additional factory method
for variables. Note that, unlike the previous attempt, \lstinline{VarExpAlg[E]}
is a subtype of \lstinline{ExpAlg[E]}, thus the type-refinement of the
field is allowed. Now, the code for parsing variables (\lstinline{pVar}) can
call \lstinline{alg.varE}. The following code illustrates how to use
the parser from a client perspective:

\lstinputlisting[linerange=48-51]{../Scala/Parser/src/PaperCode/Sec4OA/Code3.scala}% APPLY:linerange=EXT_OA_PARSER_CLIENT

In the client code shown above, we first need to choose a concrete
object algebra to initialize the \lstinline{alg} field in \lstinline{VarExprOAParser}. Here we pick the
pretty-printing algebra \lstinline{VarExprPrint}, but any other object
algebra that implements \lstinline{VarExprAlg} would work.
With an instance of \lstinline{VarExprOAParser} in hand, we can call
\lstinline{pE} to obtain the parser to feed to the \lstinline{parse} method.
The result shows that such a pattern provides modular parsing.

@@

Figure~\ref{fig:multi} illustrates the corresponding Scala code
that extends the Object Algebra interface, pretty-printing operation and parser. We use two type parameters \inlinecode{E} and \inlinecode{T} for expressions and types. They guarantee that invalid terms such as \inlinecode{int + int} will be rejected by the parser.
Besides lexing, the trait \inlinecode{TypedLamOAParser} also introduces parsers for types, and the new case for expressions.
We use \inlinecode{pTypedLamT} and \inlinecode{pTypedLamE} as copies of current \inlinecode{pT} and \inlinecode{pE}, due to the issue
with \inlinecode{super} in Scala (see discussion in Section~\ref{subsec:parsingwithoa}). \inlinecode{pT} and \inlinecode{pE} are the parsers used for performing recursion.

@@

\lstinputlisting[linerange=63-66]{../Scala/Parser/src/PaperCode/Sec4OA/Code4.scala}% APPLY:linerange=OVERVIEW_OA_MULTI_SYNTAX_CLIENT
The code works as expected to parse and pretty-print the result.
